---
title: "method"
author: "Yuta Suzuki"
date: "3/2/2022"
output: html_document
---

```{r, message=FALSE, echo=FALSE,warning=FALSE,include=FALSE}
dat <- read.xlsx("../[Python]PreProcessing/results/subInfo.xlsx")

numOfSub = dim(dat)[1]
meanAge = round(mean(dat[!is.na(dat$X2),]$X2),2)
sdAge = round(sd(dat[!is.na(dat$X2),]$X2),2)
numOfMen = length(which(dat[!is.na(dat$X4),]$X4 == 'M'))
numOfWomen = length(which(dat[!is.na(dat$X4),]$X4 == 'F'))

ind_data$numOfTrials = 0
for(iSub in sort(unique(ind_data$sub))){
  for(iLag in sort(unique(ind_data$SOA))){
    for(ivField in sort(unique(ind_data$vField))){
      d = ind_data[ind_data$sub == iSub &
                     ind_data$SOA == iLag &
                     ind_data$vField == ivField,]
      if (dim(d)[1] > 0){
      ind_data[ind_data$sub == iSub &
                 ind_data$SOA == iLag &
                 ind_data$vField == ivField,]$numOfTrials = dim(d)[1]
    }
    }
  }
}
tmp = aggregate( . ~ sub*SOA*vField, data = ind_data, FUN = "mean")
tmp$diff = 10-tmp$numOfTrials


rejectedNum = numOfSub - length(unique(ind_data$sub))
rejectedNumName = c("One","Two","Three","Four","Five","Six","Seven","Eight","Nive")
```

# Methods
### Participants
Seventy-three volunteers (`r numOfMen` men; `r numOfWomen` women; mean age = `r meanAge`, SD = `r sdAge`) participated in the experiment. `r rejectedNumName[rejectedNum]` were excluded from the analysis because they failed to fit with a psychometric curve (see Statistical Analysis section). The experiment lasted approximately 15 min, and all participants were compensated for their time (100 NOK). All experimental procedures were in accordance with the ethical principles outlined in the Declaration of Helsinki and approved by the Committee at the Oslo university. The experiment was performed in accordance with the approved guidelines of the committee and all participants provided written informed consent. Participant data and experimental scripts are available from https://github.com/suzuki970/PupilFLE.
\

### Stimulus and apparatus
The xy coordinates of the background and objects were 0.350 and 0.365 in the CIE1931 color space. The luminance of the stimuli was calibrated using a Spyder 4 Elite photometer (Datacolor Imaging Solutions, Lawrenceville, NJ), which indicated the background was 28.41 cd/m2. The luminance of the flashed and moving bars was 71.66 cd/m2. All stimuli were presented on 22 in. LCD monitor (P2210, Dell., Round Rock, US) with a resolution of 1680 x 1050 and a refresh rate of 60 Hz. The visual angle of the flashed and moving bars were 1.5° x 0.1° and 1.0° x 0.1° respectively. The trajectory of the moving bar was from 4.5° to 2.5° away from the center of the monitor. The bar moved horizontally toward within 500 ms so that the moving speed was 4°/s and. The flashed object was located at 2.5° x 2.75° from the center. The fixation point of 0.2° was located at the center. Each participant’s chin was fixed at a viewing distance of 600 mm. The task was conducted in a darkroom and executed by Experiment Center (SMI, Berlin, Germany).
\

### Procedure
The experiment was beginning with a five-point eye calibration. Figure 1 illustrates the experimental procedure. In each trial, a fixation point presented for 2,000 ms prior to the presentation of the stimulus. The moving bar appeared flash-lag stimulus at left/right for 50 ms and then started moving toward the center of the screen. During the presentation, the flashed bar appeared for 16 ms at each 8 SOA SOAs of -83.3, -66.7, -50.0, -33.3, -16.7, 0.0, 16.7 and 33.3 ms relative to the middle of presentation (i.e., 250 ms). Then, participants asked to answer whether they perceived the moving bar at the left or right of flashed bar using a keypad (Figure 1A). Each trial was separated by an inter-stimulus interval (ISI) of 2,000 ms. In the first block, the stimulus presented on LVF side of the screen for half of the participants and on RVF for another half. The second block was tested by the opposite visual field from the first block. Thus, total number of trials were 160 (2 visual fields(VFs) × 8 SOAs(or Lags?) × 10 repetitions).
\

### Recording and analysis of pupil size
Pupil size and gaze position were measured by a SensoMotoric Instruments RED500 (SMI, Berlin, Germany) eye-tracking system at a sampling rate of 60 Hz. An eye movement was measured at a resolution of about 0.01°. Pupil data during eye-blinks, obtained as the values of zero in the data and more than ±3 standard deviation of the first derivative of pupil data within each session and participant, were interpolated by piecewise cubic hermite interpolation. The trial including the pupil changes in more than 12 mm/s were excluded from the analysis (the mean rejected trials were 
`r round(mean(tmp$diff),3)` and SD = `r round(sd(tmp$diff),3)` out of 10 trials). The analyses in the present study were based on pupil diameters calculated in z-score (z) within the session for each participant. Baseline pupil size was computed as an average of data collected during the fixation period prior to stimulus onset from -500 ms to 0 ms (i.e., presentation onset). The pupillary data in each trial were baseline-corrected by subtracting the baseline pupil size, following which smoothing of each data point with ± 30 ms. Across SOAs, the pupillary response was averaged from the presentation period of stimulus onset to offset.
\

### Statistical analysis
The averaged probability of participants answering whether the moving bar was perceived ahead of flashed bars was fit with a psychometric curve using a maximum-likelihood logistic function. We estimated a Point of subjective equality (PSE) as the flash-lag effect at the probability of 0.5. After collecting PSE data at LVF and RVF for all observers, we performed pairwise t-test on a PSE between the visual fields. To statistically assess whether the FLE differed between VFs, PSE in each visual field were first bootstrapped 2000 times to estimate the mean and confidence interval. Mean pupillary changes are subjected to a two-way repeated-measures analysis of variance (ANOVA) with VFs and Lags as the within- subject factor. Pairwise comparisons of the main effects were corrected through multiple comparisons using the Bonferroni-Holm method. The level of statistical significance was set to p < 0.05 for all analyses. Effect sizes were given as partial $\eta^2$; $\eta^2_p$ for ANOVAs and as Cohen’s $d_z$ for $t$-tests {Cohen.1989}. Greenhouse-Geisser corrections were performed when the results of Mauchly’s sphericity test were significant. To quantify the evidence in the data, we performed Bayesian paired t-tests and computed Bayes factors (BF) using a Cauchy prior width of r = 0.707 for effect size (v0.9.12-4.2) {Morey.2018kwf} for the R software (Version 3.6.3) {Team.2016}. We reported Bayes Factor (BF) estimating the relative weight of the evidence in favor of $H_1$ over $H_0$ as $BF_{10}$.

To compare the mean RT across SOA, we used a linear and nonlinear mixed-effects modeling with participant as a random effect to fit the data using the lme4 packages {Bates.2015}. 
In the analysis, we fitted the following two models to assess whether the pupil change variability ($Y$) can be explained by the lag ($X$) using a second-order polynomials or monotonic fitting. 


Model 1 : $Y = \beta_0 + \beta_1X$

Model 2 : $Y = \beta_0 + \beta_1X + \beta_2X^2$


where $\beta$ as regression coefficients. The models were quantified using the Akaike information criterion (AIC), which specifies the evidence of goodness of fit for a model.

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
# ### ROC curve
# For the baseline correction of pupillary response, the first 0.2 s served as a baseline after the stimulus onset (the baseline period is shown as the dotted line in Fig. 4), and we subtracted this baseline from any samples recorded after stimulus presentation. Then, the time course of pupillary responses for each VF location and stimulus pattern was averaged across all repeated trials. Next, we calculated early and late components 36,37 to assess pupillary light reflex (PLR) responses and their “recovery” after the PLR. First, we averaged the pupil responses across all locations data with time series for each participant. Second, we computed the pupil slope using second-order accurate central differences to obtain the maximum pupil constriction latency (MPCL). The MPCL was defined as an initial local maximum negative value of the slope separated by ≥ 0.25 s (Fig. 3). The early component was defined by the average pupil data within the window of MPCL ± 0.25 (Fig. 5A, red shaded area). The late component, defined as the area under the curve (AUC), was computed as follows: 
# 
# $AUC = \sum_{i=max}^{min}x_i - x_{min}$ 
# 
# where x represents pupil size at i seconds after stimulus onset. The AUC represents a total pupil diameter increase from the PLR toward baseline pupil size (i.e., a pupil size “recovery” back to baseline).
```


